\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-18 paper/paper.tex
conclusion done

Using this improved algorithm, the robot was indeed able to create a better mapping and close up one of the holes from the previous mapping while reducing the size of the holes in the other cases.\\

\ednote{add the rest if there is more}

Unfortunately, this research could not be tested in a real life scenario, and we can therefore not make any claims about its real-life performance. We strongly recommend creating a better algorithm for obstacle avoidance before testing this algorithm in a real life scenario.\\

In conclusion, this algorithm successfully creates a mapping of a reef structure. As pointed out in \autoref{sec:eval}, there are some improvements that could be made to make the mapping even better. As is the mapping is already very good and almost complete. Depending on the requirements for the level of completeness of the mapping, this research might already be enough to give satisfactory results in a real-life scenario.\\

>>>>

Using this improved algorithm, the robot was indeed able to create a better mapping and close up one of the holes from the previous mapping while reducing the size of the holes in the other cases. These other cases were at spots on the side of elevated reef structures. To further improve our algorithm, we therefore added horizontal rotational movements to the algorithm in order to see the sides of the structures around us. This filled most of the remaining holes. The only hole that remained in the map is on the top of an elevated reef structure. To remove it, we would need to add vertical rotations as well.\\

Unfortunately, this research could not be tested in a real life scenario, and we can therefore not make any claims about its real-life performance. We strongly recommend creating a better algorithm for obstacle avoidance before testing this algorithm in a real life scenario. We also would suggest that we develop an algorithm to ensure that we only rotate the robot when absolutely necessary which then predominantly only rotates the sensors.\\

In conclusion, the created algorithm successfully creates a mapping of a reef structure. As pointed out in \autoref{sec:limitations}, there are some improvements that could be made to make the mapping even better. As is the mapping is already very good and almost complete. Depending on the requirements for the level of completeness of the mapping, this research might already be enough to give satisfactory results in a real-life scenario.\\
